---
title: "jbkmisc"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(jbkmisc)
library(printr)
library(lubridate)
```

[![Travis-CI Build Status](https://travis-ci.org/jbkunst/jbkmisc.svg?branch=master)](https://travis-ci.org/jbkunst/jbkmisc)

## date

* `ym_to_date`
```{r}
ym_to_date(ym = c(200902, 201912), day = 1)
```

* `ym_diff`

```{r}
ym_diff(ym = c(200902, 201912), ym2 = c(200901, 201712))
```

* `ym_div`

```{r}
year <- format(ymd(20170101) + months(0:11), "%Y%m")
year

ym_div(year, d = 3)

ym_div(year, d = 4)
```

## dplyrs

* `ccount`
```{r}
ccount(iris, Species)
```


## shiny
* `get_my_local_ip`

```{r}
get_my_local_ip()
```

## Workflow
* `wf_create_folders`: crate data, code and output folder.

## ggtheme
* `theme_jbk`

## blog
* `spin_jekyll_post`: My custom spin r file to md and move the widgets, etc.
* `blog_set_chunk`: Set opt chunk with my preferences
* `giphy`: Put a giphy image given the id.

## databases
* `sqlQuery`: A wrapper for `RODBC::sqlQuery` but adding `tbl_df` class.
* `sqlquery2`: Do a sqlQuery given a channel, a table name and fields. If 
there are a sum, count etc, aumatically do the group by with the other 
fields
