---
title: "jbkmisc"
output:
  github_document:
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
library(jbkmisc)
library(printr)
library(lubridate)
```

[![Travis-CI Build Status](https://travis-ci.org/jbkunst/jbkmisc.svg?branch=master)](https://travis-ci.org/jbkunst/jbkmisc)

## Why? What?

Idk. Just things I need sometimes, just helpers for my __laziness__.

## Installation

```
source("https://install-github.me/jbkunst/jbkmisc")
```

## date

* `ym_to_date`
```{r}
ym_to_date(ym = c(200902, 201912), day = 1)
```

* `ym_diff`

```{r}
ym_diff(ym = c(200902, 201912), ym2 = c(200901, 201712))
```

* `ym_div`

```{r}
year <- format(ymd(20170101) + months(0:11), "%Y%m")
year

ym_div(year, ng = 3)

ym_div(year, ng = 4)
```

## dplyrs

* `countp`

```{r}
countp(mtcars, cyl)
countp(mtcars, cyl, am)
```


* `ccount`
```{r}
ccount(iris, Species)
```


## shiny
* `get_my_local_ip`

```{r}
get_my_local_ip()
```

## Workflow
* `wf_create_folders`: crate data, code and output folder.

## ggtheme

* `theme_jbk`:
  - Based on `hrbrthemes::theme_ipsum`
  - Soft gridline color
  - Legend at top for more horizontal space.

```{r}
library(ggplot2)
library(dplyr)
library(viridis)

data("diamonds")
d <- diamonds %>% 
  filter(color %in% c("E", "J", "H")) %>% 
  filter(cut %in% c("Ideal", "Premium", "Very Good")) %>% 
  sample_n(10000)
theme_set(theme_jbk())

ggplot(d, aes(carat, price)) + 
  geom_point(aes(color = clarity), size = 0.1) + 
  geom_smooth() + 
  scale_y_continuous(labels = scales::dollar) + 
  scale_color_viridis(discrete = TRUE) + 
  facet_grid(cut ~ color, scales = "free") + 
  labs(
    title = "This is a Title",
    subtutle = "This is a longer subtitle",
    caption = "A caption which nobody read but it looks important"
  )
```

* `ggsav` and `filename_gen`: Automatic generation file names given a pattern
to save without worry about names :D.

## blog & presentations
* `spin_jekyll_post`: My custom spin r file to md and move the widgets, etc.
* `blog_set_chunk`: Set opt chunk with my preferences
* `giphy`: Put a giphy image given the id.
* `ico`:

```{r}
ico("tv", "red")
R()
```


## databases
* `sqlQuery2`: A wrapper for `RODBC::sqlQuery` but adding `tbl_df` class.
* `sqlquery2`: Do a sqlQuery given a channel, a table name and fields. If 
there are a sum, count etc, aumatically do the group by with the other 
fields
* `sqlFecth2`: Do the same as `sqlFecth` but fixes the `is.POSIXct ambiguous format`
